---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 8,
  fig.asp = 0.8,
  out.width = "80%"
)
```

# rbccovideda

<!-- badges: start -->
[![codecov](https://codecov.io/gh/UBC-MDS/rbccovideda/branch/master/graph/badge.svg?token=BHMAm2mkUK)](https://codecov.io/gh/UBC-MDS/rbccovideda)
[![R-CMD-check](https://github.com/UBC-MDS/rbccovideda/workflows/R-CMD-check/badge.svg)](https://github.com/UBC-MDS/rbccovideda/actions)
<!-- badges: end -->

**Authors**: Lianna Hovhannisyan, John Lee, Vadim Taskaev, Vanessa Yuen

The British Columbia Center for Disease Control (BCCDC) manages a range of provincial programs and clinics that contribute to public health and help control the spread of disease in BC. It administers and distributes the latest daily data on COVID-19 in British Columbia, which it provides in csv format along case-, lab- and regional-specific features as well as in comprehensive ArcGIS format via the [COVID-19 webpage](http://www.bccdc.ca/health-info/diseases-conditions/covid-19/data) (under "Download the data"). This package leverages daily case-specific COVID-19 data, allowing users to conveniently download the latest case data, and - per specified date range interval - compute several key statistics, visualize time series progression along age-related and regional parameters, and generate exploratory data analysis in the form of histogram figures supporting on-demand analysis. COVID-19 case detail parameters extracted using this package:

-   Reported_Date (in YYYY-MM-DD format)
-   HA (provincial health region, e.g., "Vancouver Coast Health")
-   Sex (M or F)
-   Age_Group (reported along 10-yr age group bins, e.g., "60-69")
-   Classification_Reported (diagnosis origin, e.g., "Lab-diagnosed")

## Installation

You can install the development version of `rbccovideda` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/rbccovideda")
```

## Package Functions

-   `get_data()`

    -   This function downloads the latest detailed daily case-specific COVID-19 from BCCDC's dedicated [COVID-19 homepage](http://www.bccdc.ca/health-info/diseases-conditions/covid-19/data). It returns a dataframe containing the extracted raw data.

-   `show_summary_stat()`

    -   This function computes summary statistics from the available case-specific parameters, such as age-related and regional aggregate metrics. It returns a dataframe listing key identified summary statistics specified per the time interval queried.

-   `plot_line_by_date()`

    -   This function returns a line chart plot of daily case counts, based on parameters and grouping selected by the user, per the time interval queried.

-   `plot_hist_by_cond()`

    -   This function returns a histogram plot based on parameters and grouping selected by the user, per the time interval queried, allowing for on-demand exploratory data analysis.

## Usage

`rbccovideda` can be used to download and compute summary statistics, generate exploratory data analysis histogram plots, and plot time series chart data as follows:

```{r example}
## load library
library(rbccovideda)
library(dplyr, warn.conflicts = FALSE)
```

To download and save data from BCCDC, use `get_data()`
```{r}
all_data <- get_data()
head(all_data)
```
To generate summary statistics, call `show_summary_stat(startDate, endDate)`
```{r}
summary <- show_summary_stat("2022-01-01", "2022-01-31")
# to show the 15-columns tibble in a nice way
glimpse(summary)
```
To plot a histogram by Age, use `plot_hist_by_cond("2021-01-01", "2021-12-31", "Age")`
```{r}
plot_hist_by_cond("2021-01-01", "2021-01-30", "Age")
```


To plot a time-series line chart, use `plot_line_by_date(startDate, endDate)`
```{r}
plot_line_by_date("2021-01-01", "2021-01-30")
```


## **Role within R Ecosystem**

Given the relatively adequate accessibility of latest aggregate COVID-19 data combined with its persistent impact on socio-economics since early 2020, there are some 40 related packages found in CRAN at time as of January 2022. Examples of API wrapper packages that retrieve COVID-19 data include [canadacovid](https://github.com/taylordunn/canadacovid) and [covidregionaldata](https://github.com/epiforecasts/covidregionaldata/), while others provide functions to retrieve data, display summary statistics and generate plots, such as [nCov2019](https://github.com/YuLab-SMU/nCov2019) and [covid19.analytic](https://github.com/mponce0/covid19.analytic). In contrast to these existing packages, `rbccovideda` provides a simple user interface that focuses on the localized provincial context of British Columbia, utilizing features specific to BCCDC's data administration conventions for generating a quick overview and on-demand analysis of trends and statistics pertaining to age-related and regional case characteristics.


## Contributing

Interested in contributing? Check out the contributing guidelines. Please note that this project is released with a Code of Conduct. By contributing to this project, you agree to abide by its terms.

## Contributors

Group 25 Contributors:

-   Lianna Hovhannisyan: \@liannah
-   John Lee: \@johnwslee
-   Vadim Taskaev: \@vtaskaev1
-   Vanessa Yuen: \@imtvwy

## License

The `rbccovideda` project was created by DSCI 524 (Collaborative Software Development) Group 25 within the Master of Data Science program at the University of British Columbia (2021-2022). It is licensed under the terms of the MIT license.  

## Credits

[R Packages](<https://r-pkgs.org/>), DSCI 524 Course Material (UBC MDS)
