---
title: "Introduction to rbccovideda"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rbccovideda-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = 0.8,
  out.width = "80%"
)

```

The `rbccovideda` package provides an easy way for users to access and make plots of the covid data from the British Columbia Center of Disease Control, BCCDC.

-   It provides function to download and save data from BCCDC website to a local folder.

-   It shows the summary statistics of the BC covid data within the specified date range.

-   Only a single function call is needed to generate visual plot for data within the specified date range and the specified condition.

-   The functions in this package are designed to be independent so that you can call only the one which suit your needs.

-   A copy of raw data is downloaded in each function call.

This document introduces you how to use the `rbccovideda` package in several steps.

We will start by loading the library:

```{r setup}
## load library
library(rbccovideda)
library(dplyr, warn.conflicts = FALSE)

```

# Download Data

`get_data()` downloads all available covid data (in CSV format) directly from the BCCDC website. It saves a copy of the CSV file in the /project_root/data directory. The directory will be created if it does not exist. The function returns a tibble storing the data in 5 columns.

For example, we can get all available data and save into a tibble like this:

```{r}
all_data <- get_data()
```

```{r}
head(all_data)
```

# Show Summary Statistics

`show_summary_stat` generates the summary statistics of the data and returns as a dataframe.

This function requires two input parameters `startDate` and `endDate` for specifying the date range of data interested. `startDate` and `endDate` are strings with date format in `YYYY-MM-DD.`

For example, to show the summary statistics of covid data in January 2022,

```{r}
## Show summary statistics for 2022 January
summary <- show_summary_stat("2022-01-01", "2022-01-31")


```

Note the output is a tibble of dimension 1x15.

```{r}
print("Dimension of the output : ")
print(dim(summary))

# to show the 15-columns tibble in a nice way
glimpse(summary)
```

Here is a summary of each column in the output tibble:

| Column Name              | Description                                                                               |
|--------------------------|-------------------------------------------------------------------------------------------|
| total_cases_count        | Total number of cases in the specified date range                                         |
| latest_date              | The latest date with reported cases, within the specified date range                      |
| latest_daily_cases_count | Number of cases reported in the latest_date                                               |
| max_date                 | The date with the maximum number of daily reported cases, within the specified date range |
| max_daily_cases_count    | Number of cases reported in the max_date                                                  |
| min_date                 | The date with the minimum number of daily reported cases, within the specified date range |
| min_daily_cases_count    | Number of cases reported in the min_date                                                  |
| max_age_group            | The age group with the maximum number of reported cases, within the specified date range  |
| max_age_group_count      | Number of cases reported for the max_age_group                                            |
| min_age_group            | The age group with the minimum number of reported cases, within the specified date range  |
| min_age_group_count      | Number of cases reported for the min_age_group                                            |
| max_region               | The region with the maximum number of reported cases, within the specified date range     |
| max_region_count         | Number of cases reported for the max_region                                               |
| min_region               | The region with the minimum number of reported cases, within the specified date range     |
| min_region_count         | Number of cases reported for the min_region                                               |

# Plot Histogram by Condition

The code below shows how to create a histogram with `plot_his_by_cond`.

This function requires three input parameters. `startDate` and `endDate` for specifying the date range. `startDate` and `endDate` are strings with date format in `YYYY-MM-DD.` The `condition` parameter should be either `Age` or `Region`.

For example, to create a histogram of covid cases in 2021 by Age.

```{r}
## Plot histogram by Region for all covid cases in 2021
plot_hist_by_cond("2021-01-01", "2021-12-31", "Age")
```

Or to create a histogram of covid cases in 2021 by Region.

```{r}
## Plot histogram by Region for all covid cases in 2021
plot_hist_by_cond("2021-01-01", "2021-12-31", "Region")
```

# Plot Line Chart by Date

We can also plot a time series line chart easily with the function `plot_line_by_date`.

Similarly, this function requires two mandatory input parameters. `startDate` and `endDate` for specifying the date range. `startDate` and `endDate` are strings with date format in `YYYY-MM-DD.` An optional parameter `region`, in the form of vector, can be specified to filter the data by regions.

If `region` is not specified, data of all region is included in the plot.

```{r}
## Plot line chart for all covid cases by region in 2021
plot_line_by_date("2021-01-01", "2021-12-31")
```

We can specify a list of regions to be included in the plot, by specifying in the `region` parameter.

```{r}
## Plot line chart for all covid cases in 2021, for Fraser and Vancouver Coastal only
plot_line_by_date("2021-01-01", "2021-12-31", c("Fraser", "Vancouver Coastal"))
```
